Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-18 tex/v3/appendix.tex
new

 \documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2019

% ready for submission
\usepackage{neurips_2019}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
% \usepackage[preprint]{neurips_2019}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[]{neurips_2019}

% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{neurips_2019}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

%--------------------------------------------------------------------------------------------------------------------------------%

\usepackage{xr}
\externaldocument{main}

\RequirePackage{mathrsfs, amsthm, amsmath, amsfonts, amssymb, mathtools}%
\usepackage[titletoc,title]{appendix}%
\usepackage{dsfont}%
\usepackage{caption} % 
\usepackage{subcaption}
\usepackage{float}%
\usepackage{graphicx, color}% 
\usepackage{bm}%bold equations

%% formatting appendices
\usepackage{etoolbox}
\patchcmd{\appendices}{\quad}{. }{}{}

%% tables
\usepackage{pgfplots}%
\usepackage{booktabs,multirow,array,multicol}
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}

%% algorithms
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

\usepackage{accents}
\usepackage{datenumber}
\usepackage{wrapfig}

%% sections
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{fact}{Fact}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}%[section]
\newtheorem*{notation}{Notation}%[section]
\newtheorem{discus}{Discussion}%[section]
\newtheorem{remark}{Remark}%[section]
\newtheorem{example}{Example}%[section]
\newtheorem{exs}{Examples}%[section]
\newtheorem{ca}{Cas}
\newtheorem{remarks}{Remarks}%[section]
\newtheorem{assumption}{Assumption}{\bf}{\rm}%

% math macros
\newcommand{\bigO}{\mathcal{O}}
\newcommand{\inr}[1]{\langle #1 \rangle}
\newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
\newcommand{\norm}[1]{\|#1\|}
\newcommand{\R}{{\mathbb{R}}}
\newcommand{\E}{\mathds{E}}
\newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
\newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
\newcommand*{\dt}[1]{\accentset{\mbox{\large\bfseries .}}{#1}}

%% math operators
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}
%--------------------------------------------------------------------------------------------------------------------------------%

\title{Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''}

\begin{document}

\author{%
Mokhtar Z. Alaya \\
LITIS EA4108\\
University of Rouen\\
\texttt{mokhtarzahdi.alaya@gmail.com} 
\And
Maxime Bérar\\
LITIS EA4108\\
University of Rouen\\
\texttt{maxime.berar@univ-rouen.fr} \\
\And
Gilles Gasso \\
LITIS EA4108\\
INSA, University of Rouen\\
\texttt{gilles.gasso@insa-rouen.fr} 
\And
Alain Rakotomamonjy\\
LITIS EA4108 \\
University of Rouen\\
and Criteo AI Labs, Criteo Paris \\
\texttt{alain.rakoto@insa-rouen.fr} \\
}
\maketitle

\section{Proof of Lemma~\ref{lemma_actives_sets}}

@@

\section{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}

@@

\section{Proof of Lemma~\ref{lemma_bounds_on_marginals}}

@@

\section{Proof of Proposition~\ref{proposition_error_in_marginals}}

@@

\small
\bibliography{biblio}
\bibliographystyle{plain}

\end{document}

>>>>

\subsection{Proof of Lemma~\ref{lemma_actives_sets}}

@@

\subsection{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}

@@

\subsection{Proof of Lemma~\ref{lemma_bounds_on_marginals}}

@@

\subsection{Proof of Proposition~\ref{proposition_error_in_marginals}}

@@
